\documentclass{tccv}

\DeclareUnicodeCharacter{2603}{\MultiO}

\begin{document}

\part{Emil Indzhev}

\section{Education}

\begin{yearlist}

\item{2018 -- 2021}
     {St Catherine's College, \newline
     University of Oxford, UK}
     {BA Computer Science \newline
     Final grade: 86.75/100 \newline
     Rank: First place}

\item{2013 -- 2018}
     {Baba Tonka High School of Mathematics,\newline Ruse, Bulgaria}
     {Secondary Education}

\end{yearlist}

\section{Work experience}

\begin{eventlist}

\item{November 2021 -- Ongoing}
     {Radix Trading}
     {Quantitative Technologist}

Working on real time and research technology.

\item{June 2021 -- September 2021}
     {Jane Street}
     {Quantitative Trading Intern}

Analyzed historical data about trading patterns,
participated in mock trading challenges and had a number of
trading and finance related classes. 

\item{July 2020 -- September 2020}
     {Jane Street}
     {Software Engineering Intern}

Worked on an internal tool used for managing database permissions and roles
based on specifications given by scripts.

\item{July 2019 -- September 2019}
     {Ocado Technology}
     {Software Engineering Intern}

Worked on a reinforcement learning project about training a robotic arm. Added custom features and environments to the company branch of the Robosuite simulator.

\item{September 2018 -- February 2019}
     {Musala Soft}
     {Software Developer}

Developed algorithmic problems for Musala Soft's international programming competition CodeIT.

\end{eventlist}

\section{Software skills}

\begin{factlist}

\item{Languages}{C++, C, Python, OCaml, Scala, Haskell, Java, C\#, JavaScript}
\item{Platforms}{Windows, Linux}
\item{Other}{\LaTeX, Microsoft Office, Google Sheets, Git}

\end{factlist}

\newpage

\personal
    [github.com/indjev99]
    {emil.indjev@gmail.com}

\section{Personal projects}

\begin{projectlist}

\item{Evolving Snakes}

Snakes in an environment similar to the classical game Snake are controlled by neural networks and can reproduce. The snakes evolve and varying emergent behaviors arise.

\item{Particle Structures}

Physics simulation with procedurally generated laws that lead to particles
forming interesting lattices.

\item{AIs for Board Games}

AIs for various board games, based on hard-coded heuristics, various search algorithms, or Monte Carlo approaches.

\item{IUPAC Name Generator}

Generates the scientific names of complex organic compounds according to the IUPAC specifications.

\item{Physics Simulation}

Physics simulation made up of basic building blocks. Complex physical phenomena, such as wave diffraction, appear without being preprogrammed.

\item{Kigarai}

A machine learning library for C++ built from scratch. Supports most common types of layers and activation functions, as well as adding custom ones.

\end{projectlist}

%\newpage

\section{Achievements and awards}

\subsection{At Oxford}

\begin{yearlist}

\item{2021}
     {Overall highest final grade}
     {Highest final grade for the degree of BA Computer Science}

\item{2021}
     {Best student project}
     {Best dissertation/project submitted for the degree of BA Computer Science}

\item{2021}
     {Publication in Information Processing Letters}
     {Paper title: On complementing unambiguous automata
     and graphs with many cliques and cocliques}

\end{yearlist}

\subsection{International competitions}

\begin{yearlist}

\item{2022}
     {Google Hash Code}
     {2nd place, with team Multiocular O}

\item{2020}
     {Google Hash Code}
     {Finalist, with team Eel}

\item{2018}
     {Microsoft Bubble Cup}
     {Finalist, with team nikva tikva}

\item{2017}
     {International Autumn Tournament in Informatics}
     {Bronze Medal}

\item{2017}
     {International Linguistics Olympiad}
     {Bronze Medal}

\item{2016}
     {International Autumn Tournament in Informatics}
     {Bronze Medal}

\item{2015}
     {Balkan Olympiad in Informatics}
     {Bronze Medal}

\item{2014}
     {Junior Balkan Olympiad in Informatics}
     {Gold Medal}

\item{2014}
     {International Conference on Computer Systems and Technologies}
     {Crystal Prize for Best Paper}

\end{yearlist}

\subsection{Notable national competitions}

\begin{yearlist}

\item{2018}
     {National Olympiad in Linguistics}
     {Silver Medal}

\item{2018}
     {Spring Competition in  Informatics}
     {Gold Medal}

\item{2018}
     {National Olympiad in Physics}
     {Laureate}

\item{2018}
     {National Olympiad in Informatics}
     {Gold Medal}

\item{2017}
     {Autumn Competition in Physics}
     {Silver Medal}

\item{2017}
     {Young Physicists' Tournament}
     {First Place, with team Perun}

\end{yearlist}

\newpage

\section{Other Activities}

\begin{eventlist}

\item{Ongoing}
     {Informatics and Linguistics Competitions}
     {Problem Setter and Grader}

Frequently setting problems for Bulgarian national and international competitions in informatics such as IATI. Also, occasionally setting problems for linguistics competitions, as well as grading the works of competitors.

\item{Ongoing}
     {Various Places}
     {Competitive Programming Lecturer}

Occasionally holding lectures on competitive informatics topics such as some advanced algorithms and data structures at various summer schools, academies, etc.

\end{eventlist}

\section{Language skills}

\begin{factlist}

\item{Bulgarian}{Native}
\item{English}{Fluent}
\item{Esperanto}{Basic}
\item{German}{Basic}

\end{factlist}

\end{document}
